---
title: "CodeBook"
author: "Paul G. Smith"
date: "December 25, 2015"
---

Code Book
========
This CodeBook documents the variable names and descriptions for the `TidyDataSet` created as part of my course project for Coursera Getting and Cleaning Data course (getdata-035), in December, 2015.

Just a quick overall comment here: I chose to output my data in a very narrow format. The **cleanDataSet contains 679,734 rows**; one for each combination of dimension (66) and observation (10,299). The **TidyDataSet contains 11,880 rows**; one for each combination of activty(6) * subject (30) * dimension (66).

*I also added variables that "deconstruct" the dimension names (i.e., fBodyAcc-mean()-X) into component 7 component variables (i.e., featureDomain, featureInstrument, etc.)*

Variable Names and Descriptions
------------------------------

Variable Name       | Description
--------------------|------------
activity            | Factor:  Activities performed by the subjects in this study (6 levels)
subject             | Integer: identifier of the subject who performed the activities.
feature             | Factor:  variable name from study (un-deconstructed)
featureDomain       | Factor:  indicates time or Freq(uency) domain signal for variable
featureAcceleration | Factor:  indicates acceleration signal (Body or Gravity) for variable
featureInstrument   | Factor:  indicates measuring instrument (Accelerometer or Gyroscope) for variable
featureJerk         | Factor:  indicates Jerk signal for variable
featMagnitude       | Factor:  indicates signal magnitude for the variable
featAxis            | Factor:  indicates axial signal direction (X, Y, Z) for the variable
featureMeasurement  | Factor:  inicates type of measurement (Mean or SD)
Count               | Integer: count of data points used to compute `average`
Average             | Integer: Average of each variable for each activity and each subject

Dataset structure
-----------------

```{r}
str(TidyDataSet)
```

List the key variables in the data table
----------------------------------------

```{r}
key(TidyDataSet)
```

Show a few rows of the dataset
------------------------------

```{r}
TidyDataSet
```

Summary of variables
--------------------

```{r}
summary(TidyDataSet)
```

